Traffic Aware Resource Allocation Schemes for Multi-Cell \acs{MIMO}-\acs{OFDM} Systems

### 2015-07-30 Report/wsrm_formulation.tex
updated with Nams' comment (included Manosha's comments as well) Need to update Response

Let us consider the \eqn{\ith{j}} \ac{SCA} iteration in the \eqn{\ith{i}} \ac{AO} step to find the transmit precoders by solving the subproblem \eqref{eqn-9}. Let \eqn{\{\mbf{m}^{(i)}_j, \mbf{\beta}^{(i)}_{j}\}} be the solution obtained by solving \eqref{eqn-9} in the \eqn{\ith{(j-1)}} \ac{SCA} step. In order to proceed with the iterative procedure, the operating point for the \eqn{\ith{(j+1)}} \ac{SCA} step is updated as \eqn{\tilde{\mbf{u}} = \mbf{z}^{(i)}_{j} \triangleq \{\mbf{m}^{(i)}_j, \mbf{w}^{(i-1)}_{\ast}, \mbf{\beta}^{(i)}_{j} \}}, where \eqn{\mbf{w}^{(i-1)}_{\ast}} is the receiver obtained by solving either \eqref{opt-rx} recursively or by using the \ac{MMSE} receiver \eqref{eqn-10} from the \eqn{\ith{(i-1)}} \ac{AO} step.
\begin{algorithm}
	\SetAlgoLined
	\DontPrintSemicolon
	\BlankLine
	\SetKwInput{KwInit}{Initialize}
	\KwIn{\me{a_k, \, Q_k, \, \mvec{H}{b,k,n},\; \fall b \in \mathcal{B}, \, \fall k \in \mathcal{U}, \fall n \in \mathcal{N}}}
	\KwOut{\me{\mvec{m}{l,k,n}} and \me{\mvec{w}{l,k,n} \fall l \in \set{1,2,\dotsc,L}}}
	\KwInit{\me{i=0,j=0} and \me{\tilde{\mbf{m}}_{l,k,n}} using single user beamformer satisfying power constraint \eqref{eqn-9.1d}}
	update \me{\tilde{\mbf{w}}_{l,k,n}, \tilde{\mbf{\beta}}_{l,k,n}} using \eqref{eqn-10} and \eqref{eqn-9.1c} with \me{\tilde{\mbf{m}}_{l,k,n}} \;
	\Repeat{Queue convergence or \me{i \geq I_{\max}}}{
		\Repeat{\ac{SCA} convergence or \me{j \geq J_{\max}}}{
			solve for the transmit precoders \me{\mvec{m}{l,k,n}} using \eqref{eqn-9}\;
			update \me{\tilde{\mbf{u}}_{l,k,n}} and the constraint set \eqref{eqn-8} with the newly found \me{\mvec{m}{l,k,n}} and \me{\mvec{\beta}{l,k,n}} using \eqref{eqn-wsrm-expr}\;
			$j = j + 1$\;
		}
		update the receive beamformers \me{\mvec{w}{l,k,n}} using \eqref{eqn-9--1} or \eqref{eqn-10} with the updated precoders \me{\mvec{m}{l,k,n}}\;
		$i = i + 1$, \me{j = 0}\;
	}
	\caption{Algorithm of \acs{JSFRA} scheme}
	\label{algo-1} 
\end{algorithm}

>>>>

Let us consider the \eqn{\ith{j}} \ac{SCA} iteration in the \eqn{\ith{i}} \ac{AO} step to find the transmit precoders by solving the subproblem \eqref{eqn-9}. Let \eqn{\mbf{m},\mbf{w}}, and \eqn{\mbfa{\beta}} denote the corresponding sets obtained by grouping all transmit precoders, receive beamformers and interference values respectively in the system. Let \eqn{\{\mbf{m}^{(i)}_{j}, \mbfa{\beta}^{(i)}_{j}\}} be the solution obtained by solving \eqref{eqn-9} in the \eqn{\ith{(j-1)}} \ac{SCA} step. In order to proceed with the iterative procedure, the operating point for the \eqn{\ith{(j+1)}} \ac{SCA} step is updated as \eqn{\tilde{\mbf{u}} = \mbf{z}^{(i)}_{j} \triangleq \{\mbf{m}^{(i)}_{j}, \mbf{w}^{(i-1)}_{\ast}, \mbfa{\beta}^{(i)}_{j} \}}, where \eqn{\mbf{w}^{(i-1)}_{\ast}} is the receiver obtained by solving either \eqref{opt-rx} recursively or by using the \ac{MMSE} receiver \eqref{eqn-10} from the \eqn{\ith{(i-1)}} \ac{AO} step.
\begin{algorithm}
	\SetAlgoLined
	\DontPrintSemicolon
	\BlankLine
	\SetKwInput{KwInit}{Initialize}
	\KwIn{\me{a_k, \, Q_k, \, \mvec{H}{b,k,n},\; \fall b \in \mathcal{B}, \, \fall k \in \mathcal{U}, \fall n \in \mathcal{N}}}
	\KwOut{\me{\mvec{m}{l,k,n}} and \me{\mvec{w}{l,k,n} \fall l \in \set{1,2,\dotsc,L}}}
	\KwInit{\me{i=0,j=0} and \me{\tilde{\mbf{m}}_{l,k,n}} using single user beamformer satisfying power constraint \eqref{eqn-9.1d}}
	update \me{\tilde{\mbf{w}}_{l,k,n}, \tilde{\mbf{\beta}}_{l,k,n}} using \eqref{eqn-10} and \eqref{eqn-9.1c} with \me{\tilde{\mbf{m}}_{l,k,n}} \;
	\Repeat{Queue convergence or \me{i \geq I_{\max}}}{
		\Repeat{\ac{SCA} convergence or \me{j \geq K_{\max}}}{
			solve for the transmit precoders \me{\mvec{m}{l,k,n}} using \eqref{eqn-9}\;
			update the constraint set \eqref{eqn-8} with \me{{\mbf{u}}_{l,k,n}} and \me{\mvec{m}{l,k,n}} using \eqref{eqn-wsrm-expr} and increment $j = j + 1$\;
		}
		update the receive beamformers \me{\mvec{w}{l,k,n}} using \eqref{eqn-9--1} or \eqref{eqn-10} with the updated precoders \me{\mvec{m}{l,k,n}}\;
		$i = i + 1$, \me{j = 0}\;
	}
	\caption{Algorithm of \acs{JSFRA} scheme}
	\label{algo-1} 
\end{algorithm}
